\documentclass[12pt]{article}


\addtolength{\oddsidemargin}{-.25in}
\addtolength{\evensidemargin}{-.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{0.5in}

\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amscd}
\usepackage[dvips]{graphics}
\usepackage{overpic}
\usepackage[mathscr]{euscript}
%\usepackage{graphicx}
%\usepackage[pdftex]{graphicx}
%\usepackage{epstopdf}
\usepackage{url}

\usepackage[usenames,dvipsnames]{color}
\usepackage{hyperref}

\usepackage{mdframed}
\usepackage{verbatim}

\usepackage{color}

\newcommand{\mc}[1]{{\mathcal #1}}
\newcommand{\lyxdot}{.}

\numberwithin{equation}{section}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{lemma-definition}[theorem]{Lemma-Definition}
\newtheorem{sublemma}[theorem]{Sublemma}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{disclosure}[theorem]{Disclosure}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{question}[theorem]{Question}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{remarks}[theorem]{Remarks}
\newtheorem{example}[theorem]{Example}
\newtheorem{convention}[theorem]{Convention}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{openproblem}[theorem]{Open Problem}
\newtheorem*{acknowledgments}{Acknowledgments}
\newtheorem*{examplestar}{Example}
\newtheorem*{conv}{Convention}

\newtheorem{algorithm}{Algorithm}

\newcommand{\step}[1] {\medskip \noindent {\em Step #1.\/}}

\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}

\newcommand{\eqdef}{\;{:=}\;}
\newcommand{\fedqe}{\;{=:}\;}

\renewcommand{\frak}{\mathfrak}

\newcommand{\C}{{\mathbb C}}
\newcommand{\Q}{{\mathbb Q}}
\newcommand{\R}{{\mathbb R}}
\newcommand{\N}{{\mathbb N}}
\newcommand{\Z}{{\mathbb Z}}
\newcommand{\Sp}{{\mathbb S}}
\newcommand{\A}{{\mathcal A}}
\newcommand{\op}{\operatorname}
\newcommand{\dbar}{\overline{\partial}}
\newcommand{\zbar}{\overline{z}}
\newcommand{\wbar}{\overline{w}}
\newcommand{\ubar}{\overline{u}}
\newcommand{\Spinc}{\op{Spin}^c}
\newcommand{\SO}{\op{SO}}
\newcommand{\SU}{\op{SU}}
\newcommand{\U}{\op{U}}
\newcommand{\M}{\mc{M}}
\newcommand{\Spin}{\op{Spin}}
\newcommand{\End}{\op{End}}
\newcommand{\Aut}{\op{Aut}}
\newcommand{\Hom}{\op{Hom}}
\newcommand{\Ker}{\op{Ker}}
\newcommand{\Coker}{\op{Coker}}
\newcommand{\Tr}{\op{Tr}}
\newcommand{\Lie}{\op{Lie}}
\newcommand{\SW}{\op{SW}}
\newcommand{\tensor}{\otimes}
\newcommand{\too}{\longrightarrow}
\newcommand{\vu}{\nu}
\newcommand{\neta}{\eta}
\newcommand{\Nbar}{\overline{N}}
\newcommand{\vbar}{\overline{v}}
\newcommand{\CZ}{\op{CZ}}
\newcommand{\current}{\mathscr{C}}
\newcommand{\calabi}{\mathcal{V}}

\newcommand{\feed}{-\!\!\!\hspace{0.7pt}\mbox{\raisebox{3pt}
{$\shortmid$}}\,}

\newcommand{\union}{\bigcup}
\newcommand{\intt}{\bigcap}
\newcommand{\eps}{\varepsilon}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\Fix}{\op{Fix}}

\newcommand{\define}[1]{{\em #1\/}}

\newcommand{\note}[1]{[{\em #1}]}

\newcommand{\rb}[1]{\raisebox{1.5ex}[-1.5ex]{#1}}

\newcommand{\Span}{\op{Span}}

\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}

\renewcommand{\epsilon}{\varepsilon}

\newcommand{\Sg}{\text{Sp}(2)}
\newcommand{\Sgt}{\widetilde{\text{Sp}}(2)}
\newcommand{\Df}{\text{Diff}(S^1)}
\newcommand{\Dft}{\widetilde{\text{Diff}}(S^1)}

\newcommand{\tr}{\textcolor{red}}

\begin{document}

\setcounter{tocdepth}{2}

\title{Computing Reeb dynamics on 4d convex polytopes}
\author{Julian Chaidez\footnote{Partially supported by an NSF Graduate Research Fellowship.}\;  and Michael Hutchings\footnote{Partially supported by NSF grant DMS-1708899, a Simons Fellowship, and a Humboldt Research Award.}}

\maketitle

\begin{abstract} 
We study the combinatorial Reeb flow on the boundary of a four-dimensional convex polytope. We establish a correspondence between ``combinatorial Reeb orbits'' for a polytope, and ordinary Reeb orbits for a smoothing of the polytope, respecting action and Conley-Zehnder index. One can then use a computer to find all combinatorial Reeb orbits up to a given action and Conley-Zehnder index. We present some results of experiments testing Viterbo's conjecture and related conjectures. In particular, we have found some new examples of polytopes with systolic ratio $1$.
\end{abstract}

\input{s1_introduction_and_main_results.tex}

\input{s2_type_1_reeb_orbits.tex}

\input{s3_reeb_dynamics_on_polytopes.tex}

\input{s4_quaternionic.tex}

\input{s5_dynamics_on_smoothings.tex}

\input{s6_smooth_combinatorial.tex}

\begin{appendix}

\input{a1_rotation_numbers.tex}

\end{appendix}

\begin{thebibliography}{12}

\bibitem{abhs} A. Abbondandolo, B. Bramham, U. Hryniewicz and P. Salom\~ao, {\em Sharp systolic inequalities for Reeb flows on the three-sphere\/}, Invent. Math. {\bf 211} (2018), 687--778.

\bibitem{abhs2} A. Abbondandolo, B. Bramham, U. Hryniewicz and P. Salom\~ao, {\em Systolic ratio, index of closed orbits and convexity for tight contact forms on the three-sphere\/}, Compositio Math.\ {\bf 154} (2018), 2643--2680.

\bibitem{ak} A. Abbondandolo and J. Kang, {\em Symplectic homology of convex domains and Clarke's duality\/}, arXiv:1907.07779.

\bibitem{ako} S. Artstein-Avidan, R. Karasev, and Y. Ostrover, {\em From symplectic measurements to the Mahler conjecture\/}, Duke Math. J. {\bf 163} (2014), 2003-2022.

\bibitem{artsteinostrover2014} S. Artstein-Avidan, Y. Ostrover, \emph{Bounds For Minkowski billiard trajectories in convex bodies}, IMRN {\bf 2014}, 165--193.

\bibitem{balitskiy} A. Balitskiy, {\em Equiality cases in Viterbo's conjecture and isoperimeric billiard inequalities\/}, Int. Math. Res. Not. {\bf 2020}, 1957--1978.

\bibitem{chls} K. Cieliebak, H. Hofer, J. Latschev, and F. Schlenk, {\em Quantitative symplectic geometry\/}. In Dynamics, ergodic theory, and geometry, Math. Sci. Res. Inst. Publ. {\bf 54} (2007), pp. 1--44, Cambridge University Press.

\bibitem{eh1} I. Ekeland and H. Hofer, {\em Symplectic topology and Hamiltonian dynamics\/}, Math. Z. {\bf 200} (1989), 355--378.

\bibitem{eh} I. Ekeland and H. Hofer, {\em Symplectic topology and Hamiltonian dynamics. II.}, Math Z. {\bf 203} (1990), 553--567.

\bibitem{gh} J. Gutt and M. Hutchings, {\em Symplectic capacities from positive $S^1$-equivariant symplectic homology\/}, Algebraic and Geometric Topology {\bf 18} (2018), 3537--3600.

\bibitem{ghr} J. Gutt, M. Hutchings, and V. Ramos, {\em Examples around the strong Viterbo conjecture\/}, arXiv:2003.10854, to appear in Journal of Fixed Point Theory and Applications.

\bibitem{haim-kislev} P. Haim-Kislev, {\em On the symplectic size of convex polytopes\/}, Geometric and Functional Analysis {\bf 29} (2019), 440--463.

\bibitem{hermann} D. Hermann, {\em Non-equivalence of symplectic capacities for open sets with restricted contact type boundary\/}. Pr\'{e}publication d'Orsay num\'{e}ro {\bf 32} (1998).

\bibitem{hwz} H. Hofer, K. Wysocki, and E. Zehnder, {\em The dynamics on three-dimensional strictly convex energy surfaces\/}, Ann. Math. {\bf 148} (1998), 197--289.

\bibitem{hz} H. Hofer and E. Zehnder, {\em Symplectic invariants and Hamiltonian dynamics\/}, Birkh\"auser, 1994.

\bibitem{hulong2002} X. Hu, Y. Long, \emph{Closed characteristics on non-degenerate star-shaped hypersurfaces in $\R^{2n}$} Science In China (Series A), 45 No. 8 (2002).

\bibitem{tw} M. Hutchings, {\em Taubes's proof of the Weinstein conjecture in dimension three\/}, Bull. AMS {\bf 47} (2010), 73--125.

\bibitem{qech} M. Hutchings, {\em Quantitative embedded contact homology\/}, J. Diff. Geom. {\bf 88} (2011), 231--266.

\bibitem{umberto} U. Hryniewicz, private communication, 2017.

\bibitem{irie} K. Irie, {\em Symplectic homology of fiberwise convex sets and homology of loop spaces\/}, arXiv:1907.09749.

\bibitem{kunzle} A. F. K\"unzle, {\em Singular Hamiltonian systems and symplectic capacities\/}, {\em Singularities and Differential Equations\/}, 171--187, Banach Center Publications {\bf 33}, Polish Academy of Sciences, 1996.

\bibitem{rabinowitz} P. Rabinowitz, {\em Periodic solutions of Hamiltonian systems\/}, Comm. Pure Appl. Math {\bf 31} (1978), 157--184.

\bibitem{schlenk} F. Schlenk, {\em Embedding problems in symplectic geometry\/}, Walter de Gruyter, 2005.

\bibitem{siegel} K. Siegel, {\em Higher symplectic capacities\/}, arXiv:1902.01490.

\bibitem{viterbo} C. Viterbo, {\em Metric and isoperimetric problems in symplectic geometry\/}, J. Amer. Math. Soc. {\bf 13} (2000), 411--431.

\bibitem{weinstein} A. Weinstein, {\em On the volume of manifolds all of whose geodesics are closed\/}, J. Diff. Geom {\bf 9} (1974), 513--517.

\end{thebibliography}

\end{document}














